Reanalysis Step 4: Main Effects Outcome Analysis

### 2025-08-28 reanalysis-4-outcome_analysis.qmd
wip

```{r predicted-probs}
# Use emmeans for predicted probabilities - it handles survey models properly
# We'll use the first imputed model for illustration

@@

# Get estimated marginal means for the main effect of lapse
emm_results <- emmeans(fitted_models[[1]], 
                      ~ ever_lapse_binary,
                      type = "response",  # Get probabilities not log-odds
                      weights = "proportional")  # Use observed proportions

# Display the main effect predictions
pred_df <- as.data.frame(emm_results)

@@

kable(contrasts_df |> 
      mutate(
        Contrast = "Lapsed - Not Lapsed",
        Risk_Difference = round(estimate, 3),
        SE = round(SE, 4),
        CI_Lower = round(lower.CL, 3),
        CI_Upper = round(upper.CL, 3),
        p.value = format.pval(p.value, digits = 4, eps = 0.0001)
      ) |>
      select(Contrast, Risk_Difference, SE, CI_Lower, CI_Upper, p.value),
      caption = "Main effect: Risk difference with proper variance estimation",
      col.names = c("Contrast", "Risk Difference", "SE", "Lower CI", "Upper CI", "P-value"))
```

>>>>

```{r predicted-probs}
# Use emmeans for predicted probabilities
# We'll use the first imputed model for illustration

# Get the data from the first imputation
imp_data <- imputed_datasets[[1]]
imp_data$weights <- twang_weights[[1]]

@@

# Get estimated marginal means for the main effect of lapse
# Provide the data explicitly for survey models
emm_results <- tryCatch({
  emmeans(fitted_models[[1]], 
          ~ ever_lapse_binary,
          data = imp_data,  # Explicitly provide data
          type = "response",  # Get probabilities not log-odds
          weights = "proportional")  # Use observed proportions
}, error = function(e) {
  # If emmeans fails, return NULL and explain
  warning("Could not calculate emmeans: ", e$message)
  NULL
})

# Display results if emmeans worked
if (!is.null(emm_results)) {
  pred_df <- as.data.frame(emm_results)

@@

  kable(contrasts_df |> 
        mutate(
          Contrast = "Lapsed - Not Lapsed",
          Risk_Difference = round(estimate, 3),
          SE = round(SE, 4),
          CI_Lower = round(lower.CL, 3),
          CI_Upper = round(upper.CL, 3),
          p.value = format.pval(p.value, digits = 4, eps = 0.0001)
        ) |>
        select(Contrast, Risk_Difference, SE, CI_Lower, CI_Upper, p.value),
        caption = "Main effect: Risk difference with proper variance estimation",
        col.names = c("Contrast", "Risk Difference", "SE", "Lower CI", "Upper CI", "P-value"))
} else {
  # If emmeans failed, display message
  print("Note: Predicted probabilities could not be calculated using emmeans.")
  print("The main analysis results (pooled coefficients and AMEs) above remain valid.")
}
```
